Generate data for NOBA cod ensemble modeling

### 2020-05-26 NOBAcod.Rmd
catch at age with fleet, needs testing

```{r addsnippet}

@@

@@

fgs <- NOBAom$funct.groups
biolprm <- NOBAom$biol
select_groups <- c('Mackerel', 'North_atl_cod', 'Capelin')

@@

Do we want catch by fishery? No fishery column here, check what it is doing.

>>>>

```{r addsnippet, eval=FALSE}

@@

Also added if statements to add fleets for fisheries outputs, if statements to separate output for annage and annagecatch.

@@

source(here("config/NOBA2Config.R"))
NOBAom_cod <- readRDS(file.path(d.name, paste0(scenario.name, "omlist_ss.rds")))

fgs <- NOBAom_cod$funct.group_ss
biolprm <- NOBAom_cod$biol
#select_groups <- c('Mackerel', 'North_atl_cod', 'Capelin')
select_groups <- 'North_atl_cod'

bps <- load_bps(dir = d.name, fgs = functional.groups.file, file_init = biomass.pools.file)
allboxes <- load_box(dir = d.name, file_bgm = box.file)
boxes <- get_boundary(allboxes)

@@

Do we want catch by fishery? Yes. No fishery column here, check what it is doing.
fishdiscage is empty, make sure there is no discard output from NOBA for these species.

Add a check for multiple fisheries per species, if only one then fleet irrelevant.

NOBA has multiple fleets for cod, so add fleet column to output.

Update: there is now a fleet column in output but the function is still incomplete; will not work if more than one fleet per species.
